\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-09-30 paper2015asml.tex
latest changes

Robot motion study for industrial has been primarily influenced by the need to generate smooth jerk-free trajectories that minimize wear and tear of internal parts. In recent years, there has been more interest in the generation of motions for robots working in human environments, i.e. environments with clutter and people working next to the robots. Most attention, though, has been focused on generating {\em collision-free} motions. Examples include the use of randomized planners\cite{kuffner_RRT_icra00}, trajectory optimization techniques\cite{Mrinal:2011}, and deterministic search-based techniques\cite{Cohen:2012}. Such approaches have also been modified to account for other types of constraints, e.g. dynamic constraints or process constraints arising from the task.

Human motions have been the subject of recent stufy with the intent of determining whether there are certain motor or locomotor invariants that best describe human manipulation or locomotion. Human motion has been observed to be stereo-typical~\cite{Atkeson:85}, i.e. learned motion patterns that are repeatedly used. This requires less planning of individual motions and contributes to making human motions more deterministic and predictable. The minimum jerk principle for human motions specifies that the trajectory of the human can best be represented as a motion that minimizes jerk of the hand~\cite{Flash:85}. Uno et. al.~\cite{Uno:89} used minimum torque change as a measure to explain the observed human motions. Minimizing jerk at the joint level~\cite{Rosenbaum:1995} has been another criterion used for human motion. Human motion has also been found to be optimized~\cite{Arechavaleta:2006}. Albrech et. al.~\cite{Albrecht:2011} studied the reaching motions of several subjects in table-setting situations and attempted to codify the motion using cost functions representing minimum-jerk hand motions, minimum-jerk joint motions, minimum torque change and a combination of all three. They found that no single combination of the cost functions explained the observed data completely.

@@

The MoveIt! benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities to quickly generate a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (shown in~\ref{fig:scenes}): a kitchen ({\sc Countertop}), an industrial workbench ({\sc Industrial}) and a drawer on a table ({\sc Drawer}). Multiple queries were generated in each scene for motions of the right arm of the PR2 robot. The robot was positioned in the scenes manually and motion planning queries were constructed by hand. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

The infrastructure we designed around MoveIt! allowed us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once. The analysis of these results is presented in Section~\ref{sec:analysis}.

@@

@@

\subsubsection{Demographic Questions}

Participants were asked a few demographic questions which ask about:

\begin{itemize}
\item Familiarity with videogames
\item Familiarity with robotics
\item The participant's age group: We asked whether the participant belonged to the 18-24, 25-44, 45-64, and 65+ age brackets.
\item The participant's highest education level: We asked if the particpant had a PhD/Masters, a Bachelors, Associate or High School level degree as their highest education.
\end{itemize}

None of these pieces of information were used to filter the responses we collected.

@@

The surveys were presented to users of Amazon Mechanical Turk~\cite{paolacci2010running}, who were presented with a set of demographic questions, a video, and the four scales to rate the robot's motion on the basis of elegance, efficency, smoothness and overall impression. Additionally a control question was presented with another video asking the participant about the robot's action in another different accompanying video. This served as the first satisficing trap to ensure that participants were truthfully attempting the survey. A summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}.

Mechanical Turk allows monetary compensation on completion of the survey, which we set to 15\textcent~ per survey. The expected time to complete was 1-2 minutes, which allows the participant about 1 whole minute of deliberation when assigning ratings. Additionally, the participants were allowed to replay the trajectory video repeatedly (and other features that Youtube supports). This maximum possible payout is 15.45\textdollar, or if each survey took 1.5 minutes to complete then the wage is approximately 6\textdollar~ per hour.

@@

In addition to the rating and demographic questions, a control question was incorporated to account for satisficing in online surveys~\cite{krosnick1991response}~\cite{krosnick1996satisficing}. This question served as the first counter-measure against satisficing in the survey. It asked the participant to correctly answer a question about the robot performing a simple, and easy-to-recognize motion.

The other counter-measure was to manually inspect the responses, and assess whether it agrees with the other survey respondents on a participant-by-participant and then trajectory-by-trajectory basis. The process for examining a particular participant involves seeing how his/her ratings {\em agree or disagree} with the average ratings of all the other ratings for this particular trajectory. Aggregating this over all the trajectories the participant rated gives us an idea of how much we can trust their responses and make a decision about rejecting {\em all or none} of their responses.

Another heuristic we employed in inspecting the responses was looking for the average time to complete the survey to be extremely low, which could hint at strong satisficing.

>>>>

Robot motion study for industrial has been primarily influenced by the need to generate smooth jerk-free trajectories that minimize wear and tear of internal parts. In recent years, there has been more interest in the generation of motions for robots working in human environments, i.e. environments with clutter and people working next to the robots. Most attention, though, has been focused on generating {\em collision-free} motions. Examples include the use of randomized planners\cite{kuffner2000rrt}, trajectory optimization techniques\cite{Mrinal:2011}, and deterministic search-based techniques\cite{cohen2010search}. Such approaches have also been modified to account for other types of constraints, e.g. dynamic constraints or process constraints arising from the task.

Human motions have been the subject of recent study with the intent of determining whether there are certain motor or locomotor invariants that best describe human manipulation or locomotion. Human motion has been observed to be stereo-typical~\cite{Atkeson:85}, i.e. learned motion patterns that are repeatedly used. This requires less planning of individual motions and contributes to making human motions more deterministic and predictable. The minimum jerk principle for human motions specifies that the trajectory of the human can best be represented as a motion that minimizes jerk of the hand~\cite{Flash:85}. Uno et. al.~\cite{Uno:89} used minimum torque change as a measure to explain the observed human motions. Minimizing jerk at the joint level~\cite{Rosenbaum:1995} has been another criterion used for human motion. Human motion has also been found to be optimized~\cite{Arechavaleta:2006}. Albrech et. al.~\cite{Albrecht:2011} studied the reaching motions of several subjects in table-setting situations and attempted to codify the motion using cost functions representing minimum-jerk hand motions, minimum-jerk joint motions, minimum torque change and a combination of all three. They found that no single combination of the cost functions explained the observed data completely.

@@

The MoveIt! benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities to quickly generate a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (Fig.~\ref{fig:scenes}): a kitchen ({\sc Countertop}), an industrial workbench ({\sc Industrial}) and a drawer on a table ({\sc Drawer}). Multiple queries were generated in each scene for motions of the right arm of the PR2 robot. The robot was positioned in the scenes manually and motion planning queries were constructed by hand. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

The infrastructure we designed around MoveIt! allows us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once. The analysis of these results is presented in Section~\ref{sec:analysis}.

@@

We conducted an online survey{\footnote The online survey was conducted after gaining a waiver from SRI's IRB. Our survey followed standard guidelines for privacy of participant information when conducting a survey on Mechanical Turk.}  to ask human observers to rate a variety of trajectories of the PR2 robot. The surveys were built on Amazon's Mechanical Turk~\cite{paolacci2010running}, which has become a useful tool for large online data gathering and crowd-sourced work. Each respondent in the survey was presented with a set of demographic questions, a video, and four scales to rate the robot's motion on the attributes  of elegance, efficency, smoothness and overall impression. Each respondent was expected to rate multiple trajectories but could not rate a trajectory more than once. Each video has four different views of the robot displayed simultaneously. Participants were asked a demographic questions about (a) familiarity with video games, (b) familiarity with robotics, (c) Age group: categorized as 18-24, 25-44, 45-64 and 65+ and (d) Highest Education Level: PhD/Masters/Bachelors/Associate/High School. None of these pieces of information were used to filter the responses we collected.  A summary of the rating scales used in the main survey question can be seen in Table~\ref{tab:rating_scales}.

Mechanical Turk allows monetary compensation on completion of the survey, which we set to 15\textcent~ per survey. We estimated the time that each participant would take to rate a single trajectory as 1-2 minutes. Additionally, the participants were allowed to replay the trajectory video repeatedly. The maximum possible payout for each participant is thus 15.45\textdollar (if each survey took 1.5 minutes to complete then the wage is approximately 6\textdollar~ per hour). This is standard compensation on Mechanical Turk for tasks of this type.

Respondents on Mechanical Turk are only paid if the survey organizer approves their response. A control question, asking the respondent to identify the known action of a robot in a video, served as the first satisficing trap to ensure that participants were truthfully attempting the survey (see~\cite{krosnick1991response}~\cite{krosnick1996satisficing} for more information on satisficing in survey responses. Survey responses were also manually examined to assess whether participants were responding honestly. We looked at whether participant responses were outliers when compared to the rest of the group. We also examined the average time taken by each participant to complete the survey. Overall, we found that all the participants had made a honest attempt at filling out the rating and we did not reject any of them.

@@

@@

@@
